---
output: html_document
title: "COVID-19 Data and Resources"
---

<style type="text/css">
.navbar-header  {
    margin-left: -280px !important;
}
.main-container {
  max-width: 1750px;
  margin-left: auto;
  margin-right: auto;
}
</style>

******

This webpage is an interative tool to explore a curated list of COVID-19 data sources, tools, and other resources organized by [Mathematica](https://www.mathematica.org/).

For detailed descriptions of all data sources, please visit Mathematica's [COVID-19 Curated Data, Modeling, and Policy Resources](https://www.mathematica.org/features/covid-19-curated-data-modeling-and-policy-resources) webpage.

******

The diagram below visualizes the flow of data sources (on the left) to resources that compile multiple data sources. It can be used to understand what primary data sources are underlying key COVID-19 resources. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.align='center')
library(tidyverse)
library(networkD3)
library(htmltools)
library(htmlwidgets)
library(here)
library(extrafont)
library(DT)
library(ggpubr)
library(gridExtra)
library(webshot)
extrafont::loadfonts(device = "win", quiet = TRUE)
```

```{r, fig.width = 12, fig.height=0.5, dpi = 600}
legend_labels <- c("Source data" = "#F1B51C", 
                   "Data compilation" = "#17A673")
legend_plot <- ggplot(as.data.frame(legend_labels)) + 
  geom_bar(aes(x = legend_labels, y = 1, fill = legend_labels), stat = "identity") +
  scale_fill_manual(labels = names(legend_labels), values = paste0(legend_labels), name = "") +
  theme(legend.position = "bottom", 
    legend.text = element_text(family = "Zilla Slab", 
                               size = 8, 
                               margin = margin(r = 100, unit = 'points')))

legend <- as_ggplot(ggpubr::get_legend(legend_plot))
legend
#ggsave(here::here("output/legend.png"), legend, device = "png")
```

```{r}
df <- read_csv(here("data/covid_resources.csv"))

# identify data source flag columns 
data_cols <- df %>% 
  select(-Action, -Category, - Title, -`Source name`, 
         -Link, -`Data quality notes`, -`Content`, 
         -`Date posted on Mathematica's website`, -Coverage, 
         -Aggregation, -`Update frequency/date`, -API, -`Internal?`) %>%
  names(.)

sn_df <- df %>%
  select(`Source name`, data_cols) %>% 
  mutate(Other = if_else(!is.na(Other), 1, NA_real_)) %>%
  pivot_longer(cols = data_cols, 
               names_to = "data_source", 
               values_to = "flag") %>%
  filter(!is.na(flag)) %>%
  # filter out loops 
  filter(tolower(data_source) != tolower(`Source name`)) %>% 
  # filter out those with only one link for visualization
  group_by(`Source name`) %>%
  mutate(total_sources = n()) %>%
  filter(total_sources > 1)

# define nodes
nodes <- data.frame("name" = c(sn_df$data_source, sn_df$`Source name`)) %>% unique()

# identify if nodes are raw data or compilations
nodes <- nodes %>% 
  mutate(group = case_when(
    (name %in% sn_df$data_source) & ! (name %in% sn_df$`Source name`) ~ "raw", 
     TRUE ~ "compilation" 
  ))
  
group_cols <- 'd3.scaleOrdinal() .domain(["raw", "compilation"]) .range(["#F1B51C", "#17A673"])'
 
# define links 
links <- sn_df %>% 
  select(from = data_source, to = `Source name`) %>% 
  mutate(value = 0.5) %>%
  as.data.frame() 
  
links$from_id <- match(links$from, nodes$name) - 1 
links$to_id <- match(links$to, nodes$name) - 1 

sn <- sankeyNetwork(Links = links, 
                    Nodes = nodes, 
                    Source = "from_id",
                    Target = "to_id", 
                    Value = "value", 
                    NodeID = "name", 
                    NodeGroup="group",
                    colourScale = group_cols, 
                    fontSize = 15,  
                    nodeWidth = 20, 
                    nodePadding = 20,
                    fontFamily = "Zilla Slab",
                    width = "100%", height=750,
                    sinksRight = T, 
                    margin = list("left"=400)) 

saveNetwork(sn, here::here("output/sn.html"))
#webshot(here::here("output/sn.html"),  here::here("output/sankey_network.png"))
```

```{r}
# move labels to right
onRender(sn,
  'function(el,x) {
    d3.selectAll(".node text")
      .attr("x", 6 + x.options.nodeWidth)
      .attr("text-anchor", "start");
  }'
)
```


